Kyoto VR MQP Paper First Draft

### 2019-09-09 paper.tex
expanded emulator info and added more sources

An alternative to building your app is to run your app through an emulator on
the computer you are using for development [citation needed on what an emulator
is]. Since an emulator uses software to emulate hardware, this poses two
technical issues that prevent emulators from being a proper replacement for
testing on real hardware.  Emulation is often imperfect, so glitches often
emerge in emulation that do not manifest on the actual hardware [citation
needed about emulator inaccuracies]. Secondly, (and most importantly for AR,)
it is common for emulation to be much slower compared to real hardware.

ViroReact offers a convenient ``test bed'' for rapidly testing your ViroReact
app on native hardware. In the root directory of your project, you can launch
a Node server with the command \texttt{npm start}. From here, you can input
the provided URL into the Viro Media app. This will quickly download the code,
graphics and 3D object files from the server and launch a functional version
of the app \autocite{viro-testbed2019}. This allowed us to get a real AR app
up and running on our devices much more easily than any of the other
frameworks/engines we explored. Unfortunately, the test bed app was somewhat
unreliable based on our experience; the test bed would frequently crash,
or would not be able to download the files from the Node server. The most
reliable way to test our app was to compile a binary and manually install it
onto our devices, which completely defeats the purpose of the test bed app.

>>>>

An alternative to building your app is to run your app through an emulator on
the computer you are using for development.

According to Techopedia, ``Emulation is the process of imitating a
hardware/software program/platform on another program or platform. This makes
it possible to run programs on systems not designed for
them''~\autocite{techopedia2019}. Emulators are often very useful for speeding
up development. Loading programs onto the Android emulator usually much faster
than installing the APK onto the actual device. Additionally, you can mock
almost all of the important features of an actual Android device, including
calls, text, GPS position, device rotation and more \autocite{androidemulator}.

Since an emulator uses software to emulate hardware, this poses two technical
issues that prevent emulators from being a proper replacement for testing on
real hardware.  Emulation is often imperfect, so glitches sometimes emerge in
emulation that do not manifest on the actual hardware [citation needed about
emulator inaccuracies]. Secondly, and most importantly for AR, it is common for
emulation to be much slower compared to real hardware. In a question submitted
to \textit{Compute!} magazine asking whether it is possible for a Commodore 64
to emulate MS-DOS, the editor responded ``Yes, it's possible for a 64 to emulate
an IBM PC, in the same sense that it's possible to bail out Lake Michigan with
a teaspoon.'' The editor goes on to explain ``Emulation is a complex business,
but here's one rule of thumb: The only way to successfully emulate a machine is
with a much more powerful machine''~\autocite{warick1988}. In our case,
emulating Android on a desktop operating system is closer to emulating a C64 on
an IBM PC running MS-DOS (rather than the other way around, thankfully.) The
moral is that the speed problem facing emulators is just as real as it was in
1988. Considering that AR already pushes modern phone harware to the limit,
emulation is not something is not something we wanted to struggle with. On top
of this, our testing required us to move the camera through the world at
various speeds and angles, which is simply cumbersome with a webcam and laptop.

ViroReact offers a convenient ``test bed'' for rapidly testing your ViroReact
app on native hardware without the need for an emulator. In the root directory
of your project, you can launch a Node server with the command \texttt{npm
start}. From here, you can input the provided URL into the Viro Media app. This
will quickly download the code, graphics and 3D object files from the server
and launch a functional version of the app \autocite{viro-testbed2019}. This
allowed us to get a real AR app up and running on our devices much more easily
than any of the other frameworks/engines we explored. Unfortunately, the test
bed app was somewhat unreliable based on our experience; the test bed would
frequently crash, or would not be able to download the files from the Node
server. The most reliable way to test our app was to compile a binary and
manually install it onto our devices, which completely defeats the purpose of
the test bed app.
